Irt plot extra

### 2022-03-24 manuscript.Rmd
EFA Diagram removed Supplimentary table reordered

#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives Supplimentary

@@

```{r EFAplotcode, eval=FALSE, include=FALSE}
#This chunk holds code for the EFA plot
EFAplot <- grViz("
digraph nicegraph {

graph [layout = dot,rankdir = LR, fontsize = 40]

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 40]
F5 [label = 'F5']
F4 [label = 'F4']
F3 [label = 'F3']
F2 [label = 'F2']
F1 [label = 'F1']

node [fontname = Helvetica, shape = box, fontsize = 50, height = 1]
b [label = 'item16']
c [label = 'item36']
d [label = 'item17']
e [label = 'item11']
f [label = 'item10']
g [label = 'item12']
h [label = 'item7']
i [label = 'item8']
j [label = 'item9']
k [label = 'item27']
l [label = 'item3']
m [label = 'item40']
n [label = 'item30']
o [label = 'item41']
p [label = 'item33']
q [label = 'item32']
r [label = 'item35']
s [label = 'item37']
t [label = 'item38']
u [label = 'item46']
v [label = 'item45']
w [label = 'item25']
x [label = 'item4']
y [label = 'item1']
z [label = 'item26']

# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 40]
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
}
")

export_svg(EFAplot) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Figures/EFAplot.png",dpi =600)

@@

efa.tab.ful <- cbind(efa.table[,1],efa.stems, efa.table[,2:8] )

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 3)).

@@

apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items", note = "Only loading > .30 is reported", 
          font_size = "footnotesize", escape=F,landscape = T,
           align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(efa.tab.ful))))
```

>>>>

#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives Supplementary

@@

@@

efa.tab.ful <- cbind(efa.table[,1],efa.stems, efa.table[,2:7] )

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Supplementary Table 3). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 4)).

@@

apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method", note = "Only loading > .30 is reported", 
          font_size = "footnotesize", escape=F,landscape = T,
           align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(efa.tab.ful))))
```
